---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  envir = globalenv()
)
```

# BicycleTheme2023

<!-- badges: start -->
<!-- badges: end -->

The goal of BicycleTheme2023 is to allow all Bicycle users of ggplot2 to create Bicycle-themes figures for presentations/posters/dashboards/etc.

## Installation

You can install the development version of BicycleTheme2023 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jdwells-bicycletx/BicycleTheme2023")
```
```{r source_code, echo = FALSE}
source('R/skeleton_theme.R')
source('R/check_fonts.R')
```

The first time you install this package, YOU MUST run:
```{r font, results='hide', warning=FALSE}
check_fonts()
```
This may take a minute

## Examples

This is a basic example which shows the use of one color in the theme:

```{r single_color}
library(BicycleTheme2023)
library(ggplot2)
ggplot(mtcars, aes(hp, mpg)) +
  geom_point(color = bicycle_cols('violet'),
             size = 4, alpha = .8)
```

You can reference individual colors using:

```{r index_color}
bicycle_pal('bright')(2)
```

STILL NEEDED: a function to list out the palettes and a function to list out the colors

Coloring by a continuous variable:

```{r continuous}
ggplot(mtcars, aes(wt, mpg, color = mpg)) +
  geom_point(size = 4) + theme_bicycle() + 
  scale_color_bicycle(palette = 'main', discrete = FALSE)
```

Coloring by a discrete variable:

```{r discrete}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) + theme_bicycle() +
  scale_color_bicycle(palette = 'main')
```

Filling by discrete variable:

```{r fill_discrete}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme_bicycle() +
  scale_fill_bicycle(palette = "grays")
```

TO BE ADDED: figures that show the colors and the palettes

To use in your scripts: theme_set(theme_bicycle()). Since this is a skeleton theme, you can always add ggplot2 arguments as needed
